---
title: "calculate_lateral_longitudinal_takeover_metrics"
author: "Courtney Goodridge"
date: "14/08/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preamble 

This script takes in the eye tracking time series data and processes it for creating the contour plots for gaze dispersion in the Goodridge et al (2026) manuscript. 

## Packages

```{r}
if(!require(here)) install.packages("here")
library(here)

if(!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)

if(!require(dplyr)) install.packages("dplyr")
library(dplyr)

if(!require(tidyr)) install.packages("tidyr")
library(tidyr)

if(!require(readr)) install.packages("readr")
library(readr)

if(!require(data.table)) install.packages("data.table")
library(data.table)
```

## Load current response data

```{r}
# response data frame for vehicle and eye data per trial
response.vehicle.eye <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Processed data/data_for_analysis/takeover.responses.critical.csv"))
```

## Load manual driving post-takeover

```{r}
# loading critical trial timecourse data
critical <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Processed data/data_for_analysis/dat.timecourse.critical.events.new.csv"))

# focus on just manual driving portion
# filtering manaual data and computing a common timestamp for every trial
critical.manual <- critical %>%
  dplyr::filter(vehicle_state == "manual") %>%
  dplyr::group_by(trialid) %>%
  dplyr::mutate(frame_manual = row_number()) %>%
  dplyr::mutate(timestamp_common_manual = frame_manual / 60)
  
## filter first 30 s of manual steering for each trial
critical.manual <- critical.manual %>%
  dplyr::group_by(trialid) %>%
  dplyr::filter(timestamp_common_manual <= 30)

# average lateral accelerations data for plotting
avg_lat_acc <- critical.manual %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  dplyr::arrange(trialid, timestamp_common_manual) %>%
  dplyr::group_by(n_back, ttc_criticality, timestamp_common_manual) %>%
  dplyr::summarise(lat_acc = mean(latacc))

# data saving
fwrite(avg_lat_acc, file = here::here("takeover_performance_cogload_time_budget/Data/avg_lat_acc.csv"))
  
# selecting trials in the timecourse that were used for modelling
trials <- response.vehicle.eye %>%
  dplyr::ungroup() %>%
  dplyr::select(trialid, rt)
  
critical.manual <- merge(critical.manual, trials, by = c("trialid"))

# maximum longitudinal deceleration/lateral acceleration/longitudinal and lateral jerk
lat_long_acc <- critical.manual %>%
  dplyr::arrange(trialid, timestamp_common_manual) %>%
  dplyr::group_by(trialid, n_back, ttc_criticality) %>%
  dplyr::mutate(long_jerk = cumsum(c(0, diff(longacc))), lat_jerk = cumsum(c(0, diff(latacc)))) %>%
  dplyr::summarise(max_long_jerk = min(long_jerk), max_lat_jerk = max(abs(lat_jerk)), max_long = min(longacc), mean_long = mean(longacc), max_lat = max(abs(latacc)), sd_latacc = sd(latacc), sd_steer = sd(stgAng), sdlp = sd(offset), mean_lat_acc = mean(abs(latacc))) %>%
  dplyr::ungroup() %>%
  dplyr::select(trialid, max_long_jerk, max_lat_jerk, max_long, mean_long, max_lat, sd_latacc, sd_steer, sdlp, mean_lat_acc)

# average deceleration
mean_decel <- critical.manual %>%
  dplyr::arrange(trialid, timestamp_common_manual) %>%
  dplyr::group_by(trialid, n_back, ttc_criticality) %>%
  dplyr::filter(longacc < 0) %>%
  dplyr::summarise(mean_decel = mean(longacc)) %>%
  dplyr::ungroup() %>%
  dplyr::select(trialid, mean_decel)

# merge long and lat dyanmics variables
lat_long_acc <- merge(lat_long_acc, mean_decel, by = c("trialid"))

# merge main dataframe
response.vehicle.eye <- merge(response.vehicle.eye, lat_long_acc, by = c("trialid"))
```

## Loading SD of horizontal/vertical gaze data for manual and automated driving period

```{r}
options(digits = 15)
dat.eye <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Eye data/dat.eye.full.timecourse.csv"))

# 30 s of pre-takeover eye data during automated driving
dat.eye.automation <- dat.eye %>%
  dplyr::group_by(trialid) %>%
  dplyr::filter(vehicle_state == "automation") %>%
    # calculate a common timestamp and use the first 30 s
  dplyr::mutate(timestamp_common = cumsum(c(0, diff(X.simTime))), frame = row_number()) %>%
  # find the last time stamp
  dplyr::mutate(last_time = timestamp_common[n()]) %>%
  # subtract 30 to get 30 s before the last time stamp of automation
  dplyr::mutate(last_time_minus_30_s = last_time - 30) %>%
  # filter data to get last 30 s of automation eye tracking data
  dplyr::filter(timestamp_common >= last_time_minus_30_s) %>%
  # convert to degrees and calculate gaze dispersion
  dplyr::mutate(yaw = `dgaze/unified_gaze_direction/x` * 180 / pi, pitch = `dgaze/unified_gaze_direction/y` * 180 / pi)

sd_pitch_yaw_automation <- dat.eye.automation %>%
  dplyr::summarise(sd_yaw_automation = sd(yaw), sd_pitch_automation = sd(pitch)) %>%
  # select data and trial indicator
  dplyr::select(sd_yaw_automation, sd_pitch_automation, trialid)

# merge with main dataframe
response.vehicle.eye <- merge(response.vehicle.eye, sd_pitch_yaw_automation, by = c("trialid"))

# 30 s of post-takeover eye data during manual driving
dat.eye.manual <- dat.eye %>%
  dplyr::group_by(trialid) %>%
  # filter manaul eye data
  dplyr::filter(vehicle_state == "manual") %>%
  # calculate a common timestamp and use the first 30 s
  dplyr::mutate(timestamp_common = cumsum(c(0, diff(X.simTime))), frame = row_number()) %>%
  dplyr::filter(timestamp_common <= 30) %>%
  dplyr::mutate(yaw = `dgaze/unified_gaze_direction/x` * 180 / pi, pitch = `dgaze/unified_gaze_direction/y` * 180 / pi)

# sd of pitch and yaw
sd_pitch_yaw_manual <- dat.eye.manual %>%
  dplyr::group_by(trialid) %>%
  dplyr::summarise(sd_yaw_manual = sd(yaw), sd_pitch_manual = sd(pitch)) %>%
  dplyr::select(sd_yaw_manual, sd_pitch_manual, trialid)

# merge gaze dispersion
response.vehicle.eye <- merge(response.vehicle.eye, sd_pitch_yaw_manual, by = c("trialid"))
```

## Saving new response dataframe with lateral and longitudinal measures, and gaze measures

```{r}
## Data saving 
fwrite(response.vehicle.eye, file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/Processed data/data_for_analysis/takeover.responses.critical.lat.long.csv"))
```